% --- 第一页：方法论工具箱 (Methodological Toolkit) ---
\begin{frame}{Methodological Toolkit \& Technical Expertise}
    \begin{itemize}
        \item \textbf{Structural Econometrics}: 
            \begin{itemize}
                \item Full-information Maximum Likelihood (FIML) and Simulated Likelihood.
                \item Recovering latent preference parameters ($\delta, \kappa, \gamma$).
            \end{itemize}
        \item \textbf{Experimental Design}: 
            \begin{itemize}
                \item Advanced Discrete Choice Experiments (DCE): D-efficient designs.
                \item Incentive-compatible mechanisms (e.g., BDM, Becker-DeGroot-Marschak).
            \end{itemize}
        \item \textbf{Data Analytics \& Causal Inference}:
            \begin{itemize}
                \item \textit{Social Data Analytics Minor}: Web scraping, large-scale survey management.
                \item Quasi-experimental methods: DiD, IV, RDD for health policy evaluation.
            \end{itemize}
        \item \textbf{Computational Skills}: R (Expert), Stata, Python, Qualtrics JS integration.
    \end{itemize}
\end{frame}

% --- 第二页：研究版图与未来计划 (Broader Research Agenda) ---
\begin{frame}{Broader Research Agenda: Behavioral \& Health Policy}
    \begin{itemize}
        \item \textbf{Study A: Vaccine Timing \& Behavioral Obstacles (JMP)}
            \begin{itemize}
                \item Focus: Intertemporal choice and pandemic preparedness.
            \end{itemize}
        \item \textbf{Study B: Health Shocks and Financial Decision-making}
            \begin{itemize}
                \item Utilizing experimental data to map risk preferences in developing contexts.
            \end{itemize}
        \item \textbf{Future Directions at UCSD (The "Shi Lab" Alignment)}:
            \begin{itemize}
                \item \textbf{Substance Use Policy}: Applying structural discounting models to tobacco/cannabis cessation.
                \item \textbf{Digital Health Interventions}: Using DCE to optimize nudge-based policy for marginalized groups (Medicaid).
            \end{itemize}
    \end{itemize}
    \vfill
    \begin{center}
        \textit{Goal: Bridging structural behavioral models with high-impact health policy evaluation.}
    \end{center}
\end{frame}
