\section*{Appendix B. Sample Representativeness and Census Benchmarking}
\label{app:B}
\doublespacing

This appendix evaluates the representativeness of the analytic sample ($N = 1{,}027$) by 
comparing key demographic characteristics with benchmarks from the 2020 Wuhan Census \cite{WuhanStats2021}.
Sampling of the quotes ensured the alignment in gender, age, and district of residence. As shown in 
Table~\ref{tab:census_compare_B1}, the sample closely approximates the demographic profile 
of Wuhan’s adult population. Minor differences—such as a slightly higher proportion of 
college-educated respondents—are typical of online survey panels and were further examined 
through robustness and weighting analyses.

\begin{table}[H]
\centering
\caption{Comparison of Analytic Sample with 2020 Wuhan Census Benchmarks}
\label{tab:census_compare_B1}
\begin{tabular}{p{5cm}cc}
\toprule
\textbf{Characteristic} & \textbf{Sample (\%)} & \textbf{Wuhan Census (\%)} \\
\midrule

\textit{Gender} & & \\
\quad Female & 53.0 & 51.1 \\
\quad Male   & 47.0 & 48.9 \\

\addlinespace
\textit{Age Distribution} & & \\
\quad 18--34 & 21.0 & 23.9 \\
\quad 35--44 & 31.2 & 28.6 \\
\quad 45--54 & 22.5 & 21.7 \\
\quad 55--65 & 13.2 & 14.3 \\
\quad 65+    & 12.0 & 11.5 \\

\addlinespace
\textit{Residence} & & \\
\quad Urban & 47.0 & 48.3 \\
\quad Rural & 53.0 & 51.7 \\

\addlinespace
\textit{Education Level} & & \\
\quad No formal schooling & 4.0 & 5.6 \\
\quad Primary school & 22.0 & 24.3 \\
\quad Middle school & 25.7 & 27.1 \\
\quad High school & 20.4 & 21.7 \\
\quad College/University & 15.6 & 13.4 \\
\quad Graduate degree & 11.0 & 7.9 \\

\bottomrule
\end{tabular}

\vspace{6pt}
\footnotesize
\textit{Note.} Census benchmarks are drawn from 
the Wuhan Bureau of Statistics\cite{WuhanStats2021}. Deviations follow typical patterns in online survey panels. 
Post-stratification weighting yielded mixed-logit and discount-rate estimates substantively 
identical to unweighted results (Appendix~C).
\end{table}

\begin{tcolorbox}[
    colback=gray!5,
    colframe=gray!50,
    boxrule=0.6pt,
    arc=3pt,
    left=6pt,
    right=6pt,
    top=6pt,
    bottom=6pt
]
\textbf{Summary of Sample Representativeness}

\begin{itemize}[leftmargin=1.2em]
    \item Survey sampling produced close alignment with Wuhan’s 2020 Census for gender, 
          age, and urban--rural residence.
    \item Slight upward shift in college-educated respondents is consistent with online 
          panel sampling.
    \item Pearson $\chi^2$ tests indicate no statistically significant difference between 
          sample and population distributions at the 5\% level.
    \item Weighted and unweighted mixed-logit models produced nearly identical results, 
          confirming robustness to demographic composition (see Appendix~C).
\end{itemize}
\end{tcolorbox}

To formally evaluate representativeness, Pearson $\chi^2$ tests were conducted for gender, 
age group, and residence. All tests were statistically non-significant at the 5\% level, 
indicating no systematic deviation from Wuhan’s adult population. Weighted mixed-logit 
models yielded parameters nearly identical to those in the unweighted sample, reinforcing 
the robustness of the main findings.

