\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\address{Yichao Jin \\ 
Ph.D. Candidate in Public Policy and Political Economy \\
University of Texas at Dallas \\
Richardson, TX 75080, USA \\
Email: Yichao.Jin@UTDallas.edu}

\begin{document}

\begin{letter}{The Editor \\ Economic Analysis and Policy}

\opening{Dear Editor,}

I am writing to submit our original research article titled, \textbf{``The Economic Cost of Delayed Protection: Biological Vulnerability and Intertemporal Health Decisions in Vaccination Timing,''} for consideration for publication in \textit{Economic Analysis and Policy}.

This study addresses a critical gap in health economics: the quantification of intertemporal preferences for vaccination timing. Using a discrete choice experiment conducted among 1,027 adults in Wuhan, China, we estimate formal time-discount parameters ($\kappa$ and $\delta$) and marginal willingness-to-accept (MWTA) for delayed protection. Our findings reveal that respondents strongly discount delayed vaccination and exhibit pronounced present-oriented preferences. 

Crucially, our study identifies significant heterogeneity in delay valuation based on institutional trust and health behavior. We demonstrate that waiting time functions as a regressive ``behavioral time tax,'' disproportionately burdening populations with lower institutional trust and higher medical vulnerability. For instance, respondents with low institutional trust require an MWTA of 62.3 RMB per month—more than double that of high-trust individuals (28.7 RMB). 

We believe this research is well-aligned with the scope of \textit{Economic Analysis and Policy}, as it combines rigorous economic modeling with direct policy relevance for public health logistics and incentive design. This paper has not been published elsewhere and is not under consideration by any other journal. 

Thank you for your time and for considering this manuscript. We look forward to your feedback.

\closing{Sincerely,}

\vspace{1em}
\noindent Yichao Jin \\
(Corresponding Author)

\end{letter}
\end{document}
